Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}. The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.

>>>>

The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}. The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
